Thoughts on resubmission within ARC1

### 2009-02-10 doc/client/client_technical.tex
grammatical correction

When addressing interoperability it is of paramount importance to
transparently address grid job descriptions written in different job
description languages by translating them automatically. In the
{\arclib} library this functionality is implemented in the
{\JobDescription} class. The inner representation (\texttt{JobInnerRepresentation}
class) is like to the GIN-JSDL and all elements are correspond to
variables. This variables are simple variables or complex data structures,
and private on the {\JobDescription} class.

@@

in any supported formats (currently XRSL~\cite{xrsl}, JDL~\cite{jdl},
JSDL~\cite{jsdl}), converts and stores it in a GIN-JSDL-like internal job
description format. The identification of the source's description
format is internally handled by a \texttt{JobDescriptionOrderer} class
which identifies the format by pattern matching. If the source string is
empty or the \texttt{JobDescriptionOrderer} class can not be recognize
to any formats, then it is not store nothing and return with false, else
convert and store it.

Different operations, like getting the job description in other
formats or getting job-related information, can be performed using the
description-independent functions of this class, e.g.:

@@

The {\JobDescription} class has three back-end classes, sometimes
referred to as back-end or translator modules, corresponding to the
three supported job description languages. The {\JobDescription} class
chooses the appropriate back-end module according to the pattern match
performed by the \texttt{JobDescriptionOrderer}, and uses the back-end
module for parsing and generating the job descriptions.
If the inner representation is empty or the source job descrition is not
valid, then the output is empty and return with false.
When the source format is equal with the output's format and it is not XRSL,
than set the product string with the source string. The XRSL output is
always generation from the inner representation.

Parsing is currently possible from any of the languages. JSDL, XRSL and
JDL output generation is implemented yet and even for these there are
some limitations.

The conversion mainly means a syntactical transformation and the
{\JobDescription} class can of course do nothing in those cases where
not enough data to assemble a given attribute is available or when
information can be lost because the received attribute has no
equivalent in the output language.

For the JSDL output generation the {\JobDescription} class is using
the core JSDL's capabilities amended with the JSDL-POSIX and JSDL-ARC
extensions. The loss of information is minimal in case of generating
such an output.

>>>>

When addressing interoperability it is of paramount importance to
transparently address grid job descriptions written in different job
description languages by translating them automatically. In the
{\arclib} library this functionality is implemented in the
{\JobDescription} class. The inner representation (\texttt{JobInnerRepresentation}
class) is similar to the GIN-JSDL and all elements correspond to
variables. These variables are either simple variables or complex data structures,
and are private in the {\JobDescription} class.

@@

in any supported formats (currently XRSL~\cite{xrsl}, JDL~\cite{jdl},
JSDL~\cite{jsdl}), converts and stores it in a GIN-JSDL-like internal job
description format. The identification of the source description
format is internally handled by a \texttt{JobDescriptionOrderer} class
which identifies the format by pattern matching. If the source string is
empty or the \texttt{JobDescriptionOrderer} class can not be recognized
to any formats, then it does not store anything and returns with false, otherwise
it converts and stores it.

Different operations, like getting the job description in other
formats or getting job-related information, can be performed by using the
description-independent functions of this class, e.g.:

@@

The {\JobDescription} class has three back-end classes, sometimes
referred to as back-end or translator modules, corresponding to the
three supported job description languages. The {\JobDescription} class
chooses the appropriate back-end module according to the pattern matching
performed by the \texttt{JobDescriptionOrderer}, and uses the back-end
module for parsing and generating the job descriptions.
If the inner representation is empty or the source job descrition is not
valid, then the output is empty too and returns with false.
When the source format is the same as the output format and it is not XRSL,
than we set the product string to the source string. The XRSL output is
always generated from the inner representation.

Parsing is currently possible from any of the languages. JSDL, XRSL and
JDL output generation is implemented already but even for these there are
some limitations.

The conversion mainly means a syntactical transformation and the
{\JobDescription} class can do nothing in those cases where
there are not enough data is available to assemble a given attribute or
when information can be lost because the received attribute has no
equivalent in the output language.

For the JSDL output generation the {\JobDescription} class uses
the core JSDL's capabilities amended with the JSDL-POSIX and JSDL-ARC
extensions. The loss of information is minimal in case of generating
such an output.
